### 2016-03-09 paper/stereo.tex
yasu

\section{Swarm Fusion implementations} \yasu{this section is very rough
at the moment. requires polishing. but algorithms might change as we run
experiments.}
We now explain detailed implementation of the Swarm Fusion method for
three problems in Computer Vision.

>>>>

\section{Swarm Fusion implementations} \yasu{this section is very rough
at the moment. requires polishing. but algorithms might change as we run
experiments.}
We now explain detailed implementation of the Swarm Fusion method for
three problems in Computer Vision (See Fig.~\ref{fig:problem}).
5
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/problem.pdf}
 \caption{We compare our Swarm Fusion methods against various baselines
 on the three problems in Computer Vision.}\label{fig:problem}
\end{figure}
